# What brings you here? I want to ... {#motivations}


Contributors to rOpenSci come with a wide range of motivations, which can include wanting a tangible way to participate in open science. First-time contributions may come from people in different places on a continuum of experience: from those who consider themselves newcomers exploring the landscape and trying to see where they fit, all the way to more experienced folks who know exactly what they have to offer and what they would like to contribute. 

Contributing to rOpenSci can help you build your track record of public contributions (such as code or documentation on GitHub), and may help improve your CV for job, fellowship, or award applications. 

Participation in an open source project like rOpenSci is more likely to be a lifecycle than a linear path. Having a package pass peer review for the first time can feel like a huge milestone. You might write a blog post about the package, “give back” by participating as a reviewer or mentoring someone else in their first review, or answering questions about package maintenance. But as a person becomes more experienced, they may move on. The value someone might get out of participating here will change over time and that is perfectly ok.

> ...users pursuing their own "selfish" interests build collective value as an automatic byproduct. 
> <br>
> [Tim O’Reilly on The Architecture of Participation](https://www.oreilly.com/pub/a/tim/articles/paradigmshift_0504.html)

Do you already know what value you want to get out of contributing? (It’s ok if you don’t know yet.) **To help you recognize yourself**, we’ve categorized what we think contributors to rOpenSci want into: [Discover](#discover); [Connect](#connect); [Learn](#learn); [Build](#build); [Help](#help). For each category, **we list examples of what those contributions might look like and we link to our [resources](#resources)** to help you get started. 

Choose your path. It's the journey, not the destination.



```{r child="mtv_discover.Rmd", echo=FALSE}
```

```{r child="mtv_connect.Rmd", echo=FALSE}
```

```{r child="mtv_learn.Rmd", echo=FALSE}
```

```{r child="mtv_build.Rmd", echo=FALSE}
```

```{r child="mtv_help.Rmd", echo=FALSE}
```

