# rOpenSci Resources {#resources}

Each section of this chapter describes and links to a specific rOpenSci resource with a “How to contribute” list of actions you could take. 

Not sure where to get started? 
Browse [What brings you here?](#motivations) to help you explore what you want to get out of contributing. 
Categories - [Discover](#discover), [Connect](#connect), [Learn](#learn), [Build](#build), [Help](#help) - 
each have “I want to” statements followed by examples of specific ways you can contribute. 
Each example links to a resource in this chapter to help you take action.


```{r child="rsrc_conduct.Rmd", echo=FALSE}
```

```{r child="rsrc_channels.Rmd", echo=FALSE}
```

```{r child="rsrc_commcalls.Rmd", echo=FALSE}
```

```{r child="rsrc_coworking.Rmd", echo=FALSE}
```

```{r child="rsrc_blog.Rmd", echo=FALSE}
```

```{r child="rsrc_blogguide.Rmd", echo=FALSE}
```

```{r child="rsrc_packages.Rmd", echo=FALSE}
```

```{r child="rsrc_taskviews.Rmd", echo=FALSE}
```

```{r child="rsrc_usecases.Rmd", echo=FALSE}
```

```{r child="rsrc_issues.Rmd", echo=FALSE}
```

```{r child="rsrc_devguide.Rmd", echo=FALSE}
```

```{r child="rsrc_runiverse.Rmd", echo=FALSE}
```

```{r child="rsrc_statsreview.Rmd", echo=FALSE}
```

```{r child="rsrc_contributing.Rmd", echo=FALSE}
```

<!-- Currently not evaluated, so not added (This comment can't be in the code block or rmarkdown complains-->
```{r child="rsrc_wishlist.Rmd", echo=FALSE, eval = FALSE}
```
